Ecology and Conservation Modelling Preregistration Template -- DRAFT

### 2020-06-01 analysis/preregistration_template.Rmd
Update analysis/preregistration_template.Rmd
shift in-text comment to GH
Update analysis/preregistration_template.Rmd
Split 2.2 as per Hannah's comments

HF comment: the above part of 2.2 seems like a big ask. I think we want to achieve that we will need to break it down further. Would it be sufficient to just have the bit below?

*Specify key assumptions and uncertainties underlying the model's design. Describe how uncertainty and variation will be represented in this model. This includes both exogenous uncertainties affecting the system, parametric uncertainty in input data and structural / conceptual nonparametric uncertainty in the model [@Moallemi2019].*

>>>>

## 2.2.2 Specify key assumptions and uncertainties underlying the model's design.

* Describe how uncertainty and variation will be represented in this model. This includes both exogenous uncertainties affecting the system, parametric uncertainty in input data and structural / conceptual nonparametric uncertainty in the model [@Moallemi2019].*
